\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
tweak

In this paper, we have reviewed the operation of faceted execution, a linguistic paradigm
enabling policy-agnostic programming, and showed how it may be implemented within
the Racket programming system as a library of macros. As Racket macros permit core language
forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
to be rewritten arbitrarily, it is possible to rewrite the meaning of these forms to support
a faceted semantics directly. We call our prototype system \racets: Racket with Facets.

>>>>

In this paper, we have reviewed the operation of faceted execution, a linguistic paradigm
enabling policy-agnostic programming, and showed how it may be implemented within
the Racket programming system as a library of macros. As Racket macros permit core language
forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
to be rewritten arbitrarily, it is possible to modify the meaning of these forms to support
a faceted semantics directly. We call our prototype system \racets: Racket with Facets.
